Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-08-11 ms.tex
added a time series immediately after turning LED on.

>>>>

We also show a time series immediately after where the lamp was turned on in Figure \ref{fig:indTSeriesAfterLamp}.
Unlike with HST, there is no clear ramp-up behavior.

\begin{figure*}
{\gridline{\fig{individual_stripe64_1p5_mA_rpt2.pdf}{0.99\textwidth}{}}}
\caption{Time series immediately after a lamp is turned on.}\label{fig:indTSeriesAfterLamp}
\end{figure*}
